Titeln på avhandlingens språk

### 2022-09-06 model.tex
model
impl

@@

\subsection{Model implementation}

@@

\subsection{Verifying the model}

\todo[inline]{Verification: do we need the model? (Compare to naive)}

>>>>

In the following subsections, \cref{ssec:model:exectimes,ssec:model:frames}, we explain how we design a model which fulfills these requirements.
We briefly discuss where implementations of this model can be obtained in \cref{ssec:model:impl}

@@

\subsection{Model verification}
\todo[inline]{Needs better name.}

We use Python~\num{3.10} to implement two variants of the above described model.
The first of these samples execution times directly from the empirical data from~\cite{olguinmunoz:impact2021}; we will refer to it hereafter as the \emph{empirical model}.
The second corresponds to one which first fits a theoretical \ac{exGaussian} distribution to the data before sampling; we will refer to this one as the \emph{theoretical model}.
We also implement a reference model which uses a constant execution time of \SI{5.23}{\second}, which we in turn call the \emph{naive model}.
This value of \SI{5.23}{\second} corresponds to the mean execution time of steps with the lowest level of impairment and a transition tag of \emph{no transition}.
\todo[inline]{Transition fade distance was 4 instead of 8, need to mention?}

\subsection{Model implementation}\label{ssec:model:impl}

@@

\todo[inline]{Variants?}
